---
title: "STATISTICAL INFERENCE PEER GRADED ASSIGNMENT"
author: "Rohan C Patil"
date: "20/10/2020"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---
1. SIMULATION EXERCISE

Q1.Show the sample mean and compare it to theoretical mean of the distribution.
```{r}
knitr::opts_chunk$set(echo = TRUE) 
lambda <- 0.2 
dataSimulation <- matrix(rexp(1000*40, lambda), nrow = 1000, ncol = 40)
meanDist <- apply(dataSimulation, 1, mean)
hist(meanDist, breaks = 50, main = "The distribution of 1000 averages of 40 random exponentials", xlab = "means value", ylab = "means frequency", col = "orange")
abline(v = 1/lambda, lty = 1, lwd = 5, col = "red")
legend("topright", lty = 1, lwd = 5, col = "red", legend = "Mean in Theory") 

```

## R Markdown




Q2.  Show how variable the sample is i.e wrt variance and compare it to the theoretical variance of the distribution
```{r}
distVar <- apply(dataSimulation, 1, var)
hist(distVar, breaks = 50, main = "The distribution of 1000 variance of 40 random exponentials", xlab = "Variance values", ylab = "Variance Frequencies", col = "pink")
abline(v = (1/lambda)^2, lty = 1, lwd = 5, col = "blue")
legend("topright", lty = 1, lwd = 5, col = "blue", legend = "theoretical variance") 
```

## Including Plots

You can also embed plots, for example:


Q3.Show the distribution is approximately normal.

```{r}
par(mfrow = c(3, 1))
hist(dataSimulation, breaks = 50, main = "Distribution of exponentials with lambda equals to 0.2", xlab = "Exponential", col = "red")
hist(meanDist, breaks = 50, main = "The distribution of 1000 averages of 40 random exponentials", xlab = "means values", ylab = "Means Frequency", col = "green")
NormSim <- rnorm(1000, mean = mean(meanDist), sd = sd(meanDist))
hist(NormSim, breaks = 50, main = "A normal distribution with theoretical mean and standard deviation of exponentials", xlab = "Normal variables", col = "yellow") 

```




Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
